---
title: "Challenge 2: Spicing things up with ggplot2"
author: "Lisette Abundez"
format: html
editor: source
embed-resources: true
code-tools: true
self-contained: true
echo: true
warning: false
message: false
---

For this week's Challenge, you will have three different options to explore.
I've arranged these options in terms of their "spiciness," or the difficulty of 
completing the task. **You are only required to complete one task, but if you are interested in exploring more than one, feel free!**

This is a great place to let your creativity show! Make sure to indicate what
additional touches you added, and provide any online references you used.

# Getting Set-up 

Within this document, make sure to specify that your plots are contained in
your document (`self-contained: true`) and that your code is visible to the reader (`echo: true`). If there are other formatting specifics
you would like to include, feel free to toss those in the YAML, too!

Next, create a setup code chunk to load the packages and read in the
`surveys.csv` data file exactly how you did in Lab 2.

```{r}
#| label: data
library(tidyverse)
library(here)

surveys <- read_csv(here("data", "surveys.csv"))
```
Finally, create another code chunk and paste in your code from Question 14 or Question 15 in Lab 2 -- we will be modifying the box plot of weights by species!

**Original Boxplot from Lab 2**
```{r}
#| label: boxplot

ggplot(data = surveys,
       mapping = aes(x = weight, y = species)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color = "steelblue", alpha = 0.01) 
```
# Medium: Ridge Plots

In Lab 2, you used side-by-side **boxplots** to visualize the distribution of 
weight within each species of rodent. Boxplots have [substantial flaws](https://www.data-to-viz.com/caveat/boxplot.html), namely that they
disguise distributions with multiple modes.

A "superior" alternative is the density plot. However, `ggplot2` does not allow
for side-by-side density plots using `geom_density()`. Instead, we will need to
make use of the `ggridges` package to create side-by-side density (ridge) plots.

> **For this challenge you are to change your boxplots to ridge plots. You will need to install the `ggridges` package and explore the `geom_density_ridges()` function.**

```{r}
#| label: ridge plot

library(ggridges)

ggplot(data = surveys,
       mapping = aes(x = weight, y = species)) +
  geom_density_ridges() +
  geom_jitter(color = "steelblue", alpha = 0.01) 

```
